Earth at night*\\ {\footnotesize \textsuperscript{*}The visualisation of average radiance in specific area}

### 2021-09-15 paper/main.tex
wrote papaer

@@

\begin{figure}[htbp]
    \centerline{\includegraphics[width=260pt]{images/Data_format_frontend_get.png}}
    \caption{data format}
    \label{dffg}
\end{figure}

@@

@@

\subsection{Huajie Xu} 
\textbf{Role and Tasks:} FE

\textbf{Writing contribution includs:}

>>>>

Another issue that needs attention is how to keep access token in client-side because user may not want to jump to GitHub every time when signing in. However, whether storing the token in local storage or cookie, user data is both under threaten of XSS or CSRF attack. So, in this solution, there is a JSESSIONID encrypted and stored in cookie by server, which is the real proof to obtain service. Because it is generated by the server, using the “httpOnly” flag, so JavaScript cannot read it.

@@

\begin{figure}[htbp]
    \centerline{\includegraphics[width=260pt]{images/Data_format_frontend_get.png}}
    \caption{Data format}
    \label{dffg}
\end{figure}

@@

Only relying on line chart cannot visually display all the information. Besides “radiance” and “pixels” there are still “window” representing the sampled area. Obviously, the most intuitive way to visualize area is using the map. In the map, the blue rectangles highlight the three researched areas, east of China, Middle East, and New Zealand as Fig.~\ref{wmap}.

\begin{figure}[htbp]
    \centerline{\includegraphics[width=260pt]{images/Worldmap.png}}
    \caption{World map}
    \label{wmap}
\end{figure}

Interaction is also important. User can hover the curser over points in line chart and the tooltip will pop up, showing the details, like the date and number of samples. Meanwhile, in the map, all the sampled areas will be highlighted by the red rectangles as shown in Fig.~\ref{iov}.

\begin{figure}[htbp]
    \centerline{\includegraphics[width=260pt]{images/Interaction_of_visualization.png}}
    \caption{Interaction of visualization}
    \label{iov}
\end{figure}

@@

\subsection{Huajie Xu} 
\textbf{Role and Tasks:} FE. Designed and implemented the entire fronted part of solution. Participated in frontend & backend debugging.

\textbf{Writing contribution includs:} The D, E subsections of solution summary. The B subsections of proposed solution.
